Windowed residual-minimization model reduction for dynamical systems

### 2019-10-03 main.tex
latest

\address[a]{Sandia National Laboratories,  Livermore, CA}
\begin{abstract}
This work proposes a \methodNameLower\ (\methodAcronym) model-reduction
	formulation for dynamical systems. The proposed approach minimizes the
	time-continuous full-order-model residual over a low-dimensional trial
	subspace across a sequence of time windows and addresses key deficiencies in
	existing model-reduction approaches, e.g., the time-step and time-scheme
	dependence of least-squares Petrov--Galerkin (LSPG) projection, \textit{a
	posteriori} error bounds that grow exponentially in time for Galerkin and
	LSPG projection, and the offline cost of space--time LSPG projection.
	\KTC{How do we address the offline cost of ST-LSPG?}
We consider two types of trial subspaces
	within the proposed framework:
	one that reduces only the spatial dimension of the full-order model, and one that
	reduces both the spatial and temporal dimensions of the full-order model.
	For each type of trial subspaces, we consider two different solution
	techniques: direct (i.e., discretize-then-optimize) and indirect (i.e.,
	optimize-then-discretize). Critically, we show that various instances of
	this framework yield existing model-reduction approaches, namely Galerkin,
	LSPG, and space–time LSPG projection. Numerical experiments on the
	compressible Euler and Navier--Stokes equations demonstrate that, at an
	increased computational cost, the \methodAcronym\ formulation can yield more
	accurate and physically relevant solutions than Galerkin and
	LSPG projection.  \KTC{So which is better? Should we emphasize that it is
	more general?}

@@

Simulating parameterized dynamical systems underpins many applications across
science and engineering, including engineering design, control, financial
analysis, and epidemiology. In many contexts, executing a dynamical-system
simulation at a single parameter instance---which entails the numerical
integration of a system of ordinary differential equations (ODEs)---incurs an
extremely large computational expense.  This occurs, for example, when the
state-space dimension is large (e.g., due to fine spatial resolution when
discretizing a partial differential equation) and/or when the number of time
instances is large (e.g., due to time-step limitations incurred by stability
or accuracy considerations).  When the application is time critical or many
query in nature, analysts must replace such large-scale parameterized
dynamical-system models with a low-cost approximation that makes the
application tractable.

@@

Projection-based reduced-order models (ROMs) comprise one such approximation
strategy. First, these techniques execute a computationally expensive
\textit{offline} stage that computes a low-dimensional ``trial'' subspace on
which the dynamical-system state can be well approximated (e.g., by computing
state ``snapshots'' at different time and parameter instances, by solving
Lyapunov equations). Second, these methods execute an inexpensive
\textit{online} stage during which they compute approximations to the
dynamical-system trajectory that reside on this trial subspace via a
projection process.

Model reduction for linear-time-invariant systems (and other strongly
structured dynamical systems) is quite mature \cite{wilcox_benner_rev,moore,roberts,GugercinIRKA} as system-theoretic properties (e.g., controllability,
observability, asymptotic stability, $\mathcal H_2$-optimality) can be readily
quantified and accounted for in the projection process, which yields
reduced-order models that inherit such properties.  The primary challenge for
developing reduced-order models for general nonlinear dynamical systems is
that such properties are difficult to quantitatively assess. As a result, it
is difficult to develop reduced-order models that preserve important
dynamical-system properties, which often results in inaccurate or unstable
methods.  To address this, researchers have pursued several directions that
aim to imbue reduced-order models for nonlinear
dynamical systems with properties that can improve robustness and accuracy.
These
efforts include residual-minimizing
projection that equips the ROM solution with a notion of optimality~\cite{l1,carlberg_lspg,carlberg_gnat,legresley_1,legresley_2,legresley_3,bui_resmin_steady,bui_unsteady,rovas_thesis,carlberg_thesis,bui_thesis};
space--time
projection that leads to error bounds that grow slowly in time~\cite{choi_stlspg,constantine_strom,URBAN2012203,Yano2014ASC,benner_st};
``energy-based'' inner
products that ensure non-increasing entropy in the ROM solution~\cite{rowley_pod_energyproj,Kalashnikova_sand2014};
basis-adaptation methods that improve the ROM's accuracy \textit{a
posteriori}~\cite{carlberg_hadaptation,adeim_peherstorfer,etter2019online}, stabilizing subspace rotations that account for truncated modes \textit{a priori}~\cite{basis_rotation}, structure-preserving
methods that enforce conservation \cite{carlberg_conservative_rom} or
(port-)Hamiltonian/Lagrangian structure
\cite{LALL2003304,carlberg2012spd,structurePreserveBeattie,chaturantabut2016structure,farhat2014dimensional} in the ROM; and subgrid-scale
modeling methods that aim to improve accuracy by addressing the closure
problem~\cite{san_iliescu_geostrophic,iliescu_pod_eddyviscosity,iliescu_vms_pod_ns,Bergmann_pod_vms,iliescu_ciazzo_residual_rom,Wang_ROM_thesis,wentland_apg,Wang:269133,San2018}.
We note that these techniques are often not mutually exclusive.
%Residual-minimizing projection methods are the most relevant to the current work and comprise the focus of the following review.
Residual-minimizing and space--time projection are the most relevant classes of
methods to the current work and comprise the focus of the following review.

\KTC{HERE}

@@

Residual minimization methods in model-order reduction comprise 
computing a solution within a low-dimensional trial space that minimizes some residual norm of the system of interest. Researchers have developed such residual-minimizing
model-reduction methods for both static systems (i.e., systems without
time-dependence)
\cite{legresley_1,legresley_2,legresley_3,bui_resmin_steady,rovas_thesis,carlberg_thesis,bui_thesis}
and dynamical
systems~\cite{bui_thesis,bui_unsteady,carlberg_thesis,carlberg_gnat,carlberg_lspg,carlberg_lspg_v_galerkin}.
In the latter category,
Refs.~\cite{bui_thesis,bui_unsteady,carlberg_thesis,carlberg_gnat,carlberg_lspg}
formulated the residual minimization problem for dynamical systems by
sequentially minimizing the \textit{time-discrete} full-order-model residual
(i.e., the residual arising after applying time discretization) at each time
instance on the time-discretization grid. This formulation is often referred
to as the \textit{least--squares Petrov--Galerkin} (LSPG) method.
Ref.~\cite{carlberg_lspg_v_galerkin} performed detailed analyses of this
formulation and examined its connections with Galerkin projection. Critically,
this work demonstrated that (1) under certain conditions, LSPG can be derived
from a Petrov--Galerkin projection executed on the time-continuous
full-order-model residual, and (2) LSPG and Galekrin projection are equivalent
in the limit as the time step goes to zero (i.e., Galerkin projection
minimizes the time-instantaneous full-order model residual). Numerous
numerical experiments have demonstrated that LSPG projection often yields more
accurate and stable solutions than Galerkin
projection~\cite{bui_thesis,carlberg_lspg_v_galerkin,carlberg_gnat,carlberg_thesis,parish_apg}.
The common intuitive explanation for this improved performance is that, by
minimizing the full-order-model residual over a finite time window (rather
than time instantanously), LSPG projection computes solutions that are more
accurate over a larger part of the trajectory as compared to Galerkin projection.

\KTC{Let's discuss. What specifically do we want to point out about
deficiencies in LSPG in this section? Should we also look in ST-LSPG? It seems you're trying
to say that we don't like how the time step size \textit{and} time
discretization method dictate so much about the method (I agree with this). If
so, we should structure this to include other discretize-then-optimize methods
I think. Or we could just focus on the time-step aspect (i.e., not the time
discretization method), in which case we should focus on LSPG.}
\KTC{HERE}

The LSPG approach has several shortcomings. First, the performance of LSPG depends on the
time discretization. Changing the time-step size modifies both the
time window over which LSPG minimizes the residual \textit{as well as} the
time-discretization error of the full-order model on which LSPG is based. As a
result, LSPG often yields the smallest error for an intermediate value of the
time step (see, e.g., Ref.~\cite[Figure 9]{carlberg_lspg_v_galerkin}). In
particular, as the time step decreases, the accuracy of LSPG approaches that
of Galerkin (which is often poor)\footnote{This occurs because LSPG projection
is equivalent to Galerkin projection in the limit $\Delta t \rightarrow 0$.}. 
%The accuracy of LSPG additionally degrades if the time-step size becomes too large. It is unclear if this is due to the discretization error associated with enlarging the time-step size, or rather if it is due to the size of the window the residual is being minimized over. LSPG projection additionally is
%additionally sensitive to the time discretization scheme. When used with
%explicit temporal discretization, for instance, LSPG again reverts to
%Galerkin. To gain the enhanced stability associated with LSPG, the underlying
%time-discretization scheme must be implicit with an appropriate time-step.
%%This can increase the cost of the reduced-order model, especially in the case
%where the optimal time-step required by LSPG is small. 
Second, as the LSPG approach sequentially performs residual minimization over
time-steps, is not equipped with any notion of optimality over the entire 
time domain of interest. As a result, LSPG is not equipped with \textit{a priori}
guarantees of stability or convergence, even for linear time-invariant
systems~\cite{bui_thesis}.

Researchers have pursued the development of space--time residual minimization ROMs~\cite{choi_stlspg,constantine_strom,URBAN2012203,Yano2014ASC,bui_thesis} to address this last issue. In existing space--time methods, the spatial \textit{and} temporal dependence of the state is represented in a low-dimensional space--time trial space. Space--time residual minimization approaches then comprise computing a space--time solution within this low-dimensional space--time trial space that minimizes the space--time norm of the full-order model. Space--time methods are thus equipped with a notion of optimality over the entire time domain of interest and, as a result, contain more favorable error bounds than the Galerkin and LSPG approaches.  Several drawbacks of existing space--time ROMs are that they (1) require minimizing the entire space--time residual (which can be a computationally intensive process) and (2) require the specification of a finite-dimensional temporal basis (computed, e.g., via POD applied to space--time snapshots). This latter issue is extremely relevant to the present work.  
%These space--time In these space--time ROMs, the temporal dependence of the state 
%is represented via a finite dimensional basis representation. 
%Space--time residual minimization methods can be prohibitively expensive, however, as they involve minimizing the entire space--time residual. Further, existing space--time approaches require a finite-dimensional space--time basis.

@@

This work seeks to overcome the practical challenges associated with existing
residual minimization approaches for reduced-order models. To this end, we
propose the \methodNameLower\ (\methodAcronym) method for model reduction,
which minimizes the FOM ODE residual over a sequence of arbitrarily defined
time windows. The key novelties of the work are twofold.  First, the method
minimizes the \textit{time-continuous}  residual (i.e., that associated with
the full-order model ODE). By adopting a time-continuous viewpoint, the
formulation decouples the underlying temporal discretization scheme from the
residual minimization problem, thus addressing a key deficiency of LSPG
\KTC{This is also true for ST-LSPG and maybe other discretization-based
methods? Have to check}. Time-continuous residual minimization also exposes
two different solution methods,  namely a \textit{discretize-then-optimize}
(i.e., direct) method and an \textit{optimize-then-discretize} (i.e.,
indirect) method. The second novelty is that the method sequentially minimizes
the residual over arbitrarily defined \textit{time windows} rather than
sequentially minimizing the residual over time steps or over the entire time
domain. This equips the method with additionaly flexibility that enables it to
explore more fine-grained tradeoffs between computational cost and error. We
demonstrate that this method can be viewed as a generalization of existing
methods, because particular instances of this formulation are equivalent to
Galerkin, LSPG, and space--time LSPG projection. Figure~\ref{fig:flowchart}
depicts how the proposed \methodAcronym\ method is related to existing
approaches.

The resulting approach is best viewed as a hybrid space--time method. A
variety of research has examined the formulation of space--time reduced-order
models~\cite{choi_stlspg,constantine_strom,URBAN2012203,Yano2014ASC,bui_thesis}
and the present approach displays commonalities with several such efforts.
First,~\cite{bui_thesis} briefly formulated a space--time least-squares ROM
and connected this formulation with optimal control; specifically the thesis
of optimize then discretize vs discretize then optimize was mentioned. This
formulation, however, was not fully developed and was eschewed for the
time-local residual minimization method (i.e., LSPG). The present work thus
formally develops (and extends) several of the concepts put forth
in~\cite{bui_thesis}. Next, Ref.~\cite{constantine_strom} developed a
space--time residual minimization formulation for model interpolation.  The
present work distinguishes itself from Ref.~\cite{constantine_strom} in that
(1.) in addition to trial subspaces with space--time dimension reduction, we
consider trial subspaces with spatial dimension reduction only (i.e., a classic
spatial basis is employed, opposed to a space--time basis) -- in which case
the generalized coordinates comprise a vector of functions, and (2.) we
minimize the time-continuous residual over space--time
windows;~\cite{constantine_strom} considers the solution of a fully discrete
optimization problem over the entire space--time domain. It is noted that,
similar to the current work, a time-continuous residual-minimization
formulation is used as a starting point in~\cite{constantine_strom}, and as
such thematic similarities exist between~\cite{constantine_strom} and the
present work. Lastly, Ref.~\cite{choi_stlspg} develops a space--time
formulation of the least-squares Petrov--Galerkin approach. The formulation
minimizes the \textit{fully discrete} residual over the entire space--time
domain within a given space--time trial subspace. 
%These space--time trial spaces are constructed through higher-order singular value decompositions (SVDs), such as the truncated high-order SVD. 
The present work distinguishes itself from Ref.~\cite{choi_stlspg} in that
(1.) we perform model reduction of the time-continuous system, (2.) we
consider trial subspaces with both space--time dimension reduction and spatial
dimension reduction, and (3.) residual minimization is performed over time
windows; Ref.~\cite{choi_stlspg} considers space--time bases and minimizes the
fully-discrete residual over the entire time domain.

>>>>

\address[a]{Sandia National Laboratories,  Livermore, CA}
\begin{abstract}
This work proposes a \methodNameLower\ (\methodAcronym) model-reduction
	formulation for dynamical systems. The proposed approach sequentially minimizes the
	time-continuous full-order-model residual over a low-dimensional trial
	subspace across time windows. The approach comprises a generalization 
of existing model reduction approaches; we show that various instances of
  the method recover the Galerkin,
  least-squares Petrov--Galerkin (LSPG), and space–time LSPG approaches. The approach further addresses key deficiencies in
	existing model-reduction techniques, e.g., the dependence of (space--time) LSPG 
on the time-discretization and the exponentially growing \textit{a
	posteriori} error bounds present in Galerkin and
	LSPG.
We consider two types of trial subspaces
	within the proposed framework:
	one that reduces only the spatial dimension of the full-order model, and one that
	reduces both the spatial and temporal dimensions of the full-order model.
	For each type of trial subspaces, we consider two different solution
	techniques: direct (i.e., discretize-then-optimize) and indirect (i.e.,
	optimize-then-discretize). %Critically, we show that various instances of
	%this framework yield existing model-reduction approaches, namely Galerkin,
	%LSPG, and space–time LSPG projection. 
  Numerical experiments are presented for trial subspaces with spatial dimension reduction, in where it is demonstrated that the \methodAcronym\ formulation can yield more
	accurate and physically relevant solutions than Galerkin and
	LSPG projection.

@@

Simulating parameterized dynamical systems underpins many applications across
science and engineering, including engineering design, control, financial
analysis, and epidemiology. In many contexts, executing a dynamical-system
simulation at a single parameter instance---which entails the numerical
integration of a system of ordinary differential equations (ODEs)---incurs an
extremely large computational expense.  This occurs, for example, when the
state-space dimension is large (e.g., due to fine spatial resolution when
discretizing a partial differential equation) and/or when the number of time
instances is large (e.g., due to time-step limitations incurred by stability
or accuracy considerations).  When the application is time critical or many
query in nature, analysts must replace such large-scale parameterized
dynamical-system models (which we refer to as the full-order model) with a low-cost approximation that makes the
application tractable.

@@

Projection-based reduced-order models (ROMs) comprise one such approximation
strategy. First, these techniques execute a computationally expensive
\textit{offline} stage that computes a low-dimensional ``trial'' subspace on
which the dynamical-system state can be well approximated (e.g., by computing
state ``snapshots'' at different time and parameter instances, by solving
Lyapunov equations, etc). Second, these methods execute an inexpensive
\textit{online} stage during which they compute approximations to the
dynamical-system trajectory that reside on this trial subspace via a
projection process.

Model reduction for linear-time-invariant systems (and other strongly
structured dynamical systems) is quite mature \cite{wilcox_benner_rev,moore,roberts,GugercinIRKA} as system-theoretic properties (e.g., controllability,
observability, asymptotic stability, $\mathcal H_2$-optimality) can be readily
quantified and accounted for in the projection process, which yields
reduced-order models that inherit such properties.  The primary challenge for
developing reduced-order models for general nonlinear dynamical systems is
that such properties are difficult to quantitatively assess. As a result, it
is difficult to develop reduced-order models that preserve important
dynamical-system properties, which often results in inaccurate or unstable
methods.  To address this, researchers have pursued several directions that
aim to imbue reduced-order models for nonlinear
dynamical systems with properties that can improve robustness and accuracy.
These
efforts include residual-minimizing
projection that equips the ROM solution with a notion of optimality~\cite{carlberg_lspg,carlberg_gnat,legresley_1,legresley_2,legresley_3,bui_resmin_steady,bui_unsteady,rovas_thesis,carlberg_thesis,bui_thesis,l1};
space--time
projection that leads to error bounds that grow slowly in time~\cite{choi_stlspg,constantine_strom,URBAN2012203,Yano2014ASC,benner_st};
``energy-based'' inner
products that ensure non-increasing entropy in the ROM solution~\cite{rowley_pod_energyproj,Kalashnikova_sand2014};
basis-adaptation methods that improve the ROM's accuracy \textit{a
posteriori}~\cite{carlberg_hadaptation,adeim_peherstorfer,etter2019online}, stabilizing subspace rotations that account for truncated modes \textit{a priori}~\cite{basis_rotation}, structure-preserving
methods that enforce conservation \cite{carlberg_conservative_rom} or
(port-)Hamiltonian/Lagrangian structure
\cite{LALL2003304,carlberg2012spd,structurePreserveBeattie,chaturantabut2016structure,farhat2014dimensional} in the ROM; and subgrid-scale
modeling methods that aim to improve accuracy by addressing the closure
problem~\cite{san_iliescu_geostrophic,iliescu_pod_eddyviscosity,iliescu_vms_pod_ns,Bergmann_pod_vms,iliescu_ciazzo_residual_rom,Wang_ROM_thesis,wentland_apg,Wang:269133,San2018}.
We note that these techniques are often not mutually exclusive.
%Residual-minimizing projection methods are the most relevant to the current work and comprise the focus of the following review.
Residual-minimizing and space--time projection are the most relevant classes of
methods to the current work and comprise the focus of the following review.

@@

Residual minimization methods in model-order reduction comprise 
computing a solution within a low-dimensional trial subspace that minimizes some residual norm of the system of interest. Researchers have developed such residual-minimizing
model-reduction methods for both static systems (i.e., systems without
time-dependence)
\cite{legresley_1,legresley_2,legresley_3,bui_resmin_steady,rovas_thesis,carlberg_thesis,bui_thesis}
and dynamical
systems~\cite{bui_thesis,bui_unsteady,carlberg_thesis,carlberg_gnat,carlberg_lspg,carlberg_lspg_v_galerkin}.
In the latter category,
Refs.~\cite{bui_thesis,bui_unsteady,carlberg_thesis,carlberg_gnat,carlberg_lspg}
formulated the residual minimization problem for dynamical systems by
sequentially minimizing the \textit{time-discrete} full-order-model residual
(i.e., the residual arising after applying time discretization) at each time
instance on the time-discretization grid. This formulation is often referred
to as the \textit{least--squares Petrov--Galerkin} (LSPG) method.
Ref.~\cite{carlberg_lspg_v_galerkin} performed detailed analyses of this
formulation and examined its connections with Galerkin projection. Critically,
this work demonstrated that (1) under certain conditions, LSPG can be derived
from a Petrov--Galerkin projection executed on the time-continuous
full-order-model residual, and (2) LSPG and Galerkin projection are equivalent
in the limit as the time step goes to zero (i.e., Galerkin projection
minimizes the time-instantaneous full-order model residual). Numerous
numerical experiments have demonstrated that LSPG projection often yields more
accurate and stable solutions than Galerkin
projection~\cite{bui_thesis,carlberg_lspg_v_galerkin,carlberg_gnat,carlberg_thesis,parish_apg}.
The common intuitive explanation for this improved performance is that, by
minimizing the full-order-model residual over a finite time window (rather
than time instantaneously), LSPG projection computes solutions that are more
accurate over a larger part of the trajectory as compared to Galerkin projection.
%\KTC{Let's discuss. What specifically do we want to point out about
%deficiencies in LSPG in this section? Should we also look in ST-LSPG? It seems you're trying
%to say that we don't like how the time step size \textit{and} time
%discretization method dictate so much about the method (I agree with this). If
%so, we should structure this to include other discretize-then-optimize methods
%I think. Or we could just focus on the time-step aspect (i.e., not the time
%discretization method), in which case we should focus on LSPG.}
%\KTC{HERE}

The LSPG approach, however, has several shortcomings. First, the performance of LSPG depends on the
time discretization. Changing the time-step size modifies both the
time window over which LSPG minimizes the residual \textit{as well as} the
time-discretization error of the full-order model on which LSPG is based. As a
result, LSPG often yields the smallest error for an intermediate value of the
time step (see, e.g., Ref.~\cite[Figure 9]{carlberg_lspg_v_galerkin}). In
particular, as the time step decreases, the accuracy of LSPG approaches that
of Galerkin (which is often poor)\footnote{This occurs because LSPG projection
is equivalent to Galerkin projection in the limit $\Delta t \rightarrow 0$.}. 
%The accuracy of LSPG additionally degrades if the time-step size becomes too large. It is unclear if this is due to the discretization error associated with enlarging the time-step size, or rather if it is due to the size of the window the residual is being minimized over. LSPG projection additionally is
%additionally sensitive to the time discretization scheme. When used with
%explicit temporal discretization, for instance, LSPG again reverts to
%Galerkin. To gain the enhanced stability associated with LSPG, the underlying
%time-discretization scheme must be implicit with an appropriate time-step.
%%This can increase the cost of the reduced-order model, especially in the case
%where the optimal time-step required by LSPG is small. 
Second, as the LSPG approach sequentially performs residual minimization over
time-steps, is not equipped with any notion of optimality over the entire 
time domain of interest. As a result, LSPG is not equipped with \textit{a priori}
guarantees of stability or convergence, even for linear time-invariant
systems~\cite{bui_thesis}.

Researchers have pursued the development of residual-minimizing space--time projection~\cite{choi_stlspg,constantine_strom,URBAN2012203,Yano2014ASC} to address this last issue of global optimality. 
%In existing space--time methods, the spatial \textit{and} temporal dependence of the state is represented in a low-dimensional space--time trial space. 
Space--time residual minimization approaches comprise computing a space--time solution within a low-dimensional space--time trial space that minimizes the space--time norm of the full-order model. Space--time methods are thus equipped with a notion of optimality over the entire time domain of interest and, as a result, contain more favorable error bounds than the Galerkin and LSPG approaches.  Several drawbacks of existing space--time ROMs are that they (1) require minimizing the entire space--time residual (which can be a computationally intensive process) and (2) require the specification of temporal basis (computed, e.g., via proper orthogonal decomposition applied to space--time snapshots). This latter issue precludes space--time projection methods from being used for, e.g., future state prediction. It is further worth noting that space--time projection comprises a fundamentally different approach than spatial projection. In ROMs leveraging space--time projection, the generalized coordinates (e.g., the reduced state) are a stationary vector, while the temporal dependence of the state is represented via a pre-defined basis. In ROMs leveraging spatial projection only, the generalized coordinates comprise a vector of \textit{time dependent functions}. Space--time projection executed at the time-continuous level yields an algebraic system of equations, while spatial projection executed at the time-continuous level yields a dynamical system.  
%the trial basis comprises space--time \textit{functions} that map a low-dimensional vector of generalized coordinates to the space--time solution. In spatial projection, the trial space comprises space--time functions that map a low-dimensional vector of 
%These space--time In these space--time ROMs, the temporal dependence of the state 
%is represented via a finite dimensional basis representation. 
%Space--time residual minimization methods can be prohibitively expensive, however, as they involve minimizing the entire space--time residual. Further, existing space--time approaches require a finite-dimensional space--time basis.

@@

This work seeks to overcome the practical challenges associated with existing
residual minimization approaches for reduced-order models. To this end, we
propose the \methodNameLower\ (\methodAcronym) method for model reduction. The 
\methodAcronym\ approach sequentially minimizes the FOM ODE residual over a sequence of arbitrarily defined
time windows. The key novelties of the work are threefold.  First, the method
minimizes the \textit{time-continuous}  residual (i.e., that associated with
the full-order model ODE). By adopting a time-continuous viewpoint, the
formulation decouples the underlying temporal discretization scheme from the
residual minimization problem, thus addressing a key deficiency of (space--time) LSPG. 
Time-continuous residual minimization also exposes
two different solution methods,  namely a \textit{discretize-then-optimize}
(i.e., direct) method and an \textit{optimize-then-discretize} (i.e.,
indirect) method. The second novelty is that the method sequentially minimizes
the residual over arbitrarily defined \textit{time windows} rather than
sequentially minimizing the residual over time steps or over the entire time
domain. This equips the method with additionally flexibility that enables it to
explore more fine-grained tradeoffs between computational cost and error. Finally, \methodAcronym\ is formulated for 
a general space--time trial space, thus allowing application to both classic spatial projection-only trial subspaces as well as  space--time projection trial subspaces; previous work on space--time residual minimization requires space-time trial subspaces obtained through space--time projection. We  
demonstrate that \methodAcronym\ is a generalization of existing
methods; particular instances of the formulation are equivalent to
Galerkin, LSPG, and space--time LSPG projection. Figure~\ref{fig:flowchart}
depicts how the proposed \methodAcronym\ method is related to existing
approaches.

The \methodAcronym\ approach is best viewed as a hybrid space--time method and displays 
commonalities with several related efforts. 
First,~\cite{bui_thesis} briefly formulated a space--time least-squares ROM
and connected this formulation with optimal control; specifically the thesis
of optimize-then-discretize vs discretize-then-optimize was mentioned. This
formulation, however, was not fully developed and was eschewed for 
time-local residual minimization (i.e., LSPG). The present work thus
formally develops (and extends) several of the concepts put forth
in~\cite{bui_thesis}. Next, Ref.~\cite{constantine_strom} developed a
space--time residual minimization formulation for model interpolation.  The
present work distinguishes itself from Ref.~\cite{constantine_strom} in that
(1) in addition to trial subspaces obtained via space--time projection, we
consider trial subspaces obtained via spatial projection only (i.e., a classic
spatial basis is employed, opposed to a space--time basis)% -- in which case
%the generalized coordinates comprise a vector of functions
, and (2) we
minimize the time-continuous residual over space--time
windows;~\cite{constantine_strom} considers the solution of a fully discrete
optimization problem over the entire space--time domain. It is noted that,
similar to the current work, a time-continuous residual-minimization
formulation is used as a starting point in~\cite{constantine_strom}, and as
such thematic similarities exist between~\cite{constantine_strom} and the
present work. Lastly, Ref.~\cite{choi_stlspg} develops a space--time
formulation of the least-squares Petrov--Galerkin approach. The formulation
minimizes the \textit{fully discrete} residual over the entire space--time
domain within a given space--time trial subspace. 
%These space--time trial spaces are constructed through higher-order singular value decompositions (SVDs), such as the truncated high-order SVD. 
The present work distinguishes itself from Ref.~\cite{choi_stlspg} in that
(1) we perform model reduction of the time-continuous system, (2) we
consider trial subspaces obtained via both spatial projection only and space--time projection,
 and (3) residual minimization is performed over time
windows; Ref.~\cite{choi_stlspg} considers trial subspaces obtained via space--time projection and minimizes the
fully-discrete residual over the entire time domain.
